\package{}: an \R{} package for implemetation of the ITHIM model

### 2016-09-16 manuscript/manuscript.tex
Update to ITHIM manuscript #1

\newcommand{\col}[2][red]{\textcolor{#1}{#2}}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\package}{\emph{ITHIM}}
\newcommand{\ithim}{\emph{ITHIM}}
\newcommand{\R}{\emph{R}}
\newcommand{\sgy}[1]{{\itshape\col{#1}}}
\newcommand{\XX}{\sgy{XX}}
\newcommand{\webpage}{\url{http://www.ithim.ghi.wisc.edu}}
\newcommand{\af}{\rho}
\newcommand{\mets}{MET-hrs./week}
\begin{document}
\firstpage{1}

@@

@@

@@

%\bibliographystyle{natbib}
%\bibliographystyle{bmc_article}
\bibliographystyle{mypapers}
\bibliography{ITHIM}
\end{document}

%   \begin{itemize}
%   \item The coefficient of variation was fixed at ??? for all strata
% and models.  Earlier ITHIM models estimated this as a function of
% total active tranpsort time to model the decrease in variance of
% active transport time that occurs for increasing means, i.e., fitter
% communities have less variance in active transport time.
%   \item The mean non-travel activity for the referent group was
% modeled as a variable.  The relative means across age-sex strata were
% fixed, and estimated using ATUS.
%   \item The national DALYs were stimated using the attributable
% fraction provided by the comparitive risk assesment.  The estimates
% for disease burned came from WHO and their GBD study.
%   \item Not all of the regions had the same sample size.  In fact a
% few of the regions have relativel low sample size.  Maybe we should
% put confidence intervals on our estimates.
%   \item The ITHIM model stratifies the population by sex and age using
% eight age classes.  Within each stratum active transport time is
% modeled as log-normal with mean $\hat{\mu}_{i,j}$ which is estimated
% from the National Household Transportation Survey.
%   \item Quintiles, in this case the quantiles for percentages
% $(0.1,0.3,0.5,0.7,0.9)$, are used to discretize the integral defined
% in the Comparative Risk Assesment (CRA)
%   \item
% \end{itemize}
%  ``the proportional reduction in population
% disease or mortality that would occur if exposure to a risk factor
% were reduced to an alternative ideal exposure scenario (eg. no tobacco
% use).'' \url{http://www.who.int/healthinfo/global_burden_disease/metrics_paf/en/}

>>>>

\newcommand{\col}[2][red]{\textcolor{#1}{#2}}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\package}{\emph{ITHIM}}
\newcommand{\ithim}{\emph{ITHIM}}
\newcommand{\R}{\emph{R}}
\newcommand{\sgy}[1]{{\itshape\col{#1}}}
\newcommand{\XX}{\sgy{XX}}
\newcommand{\webpage}{\url{http://www.ithim.ghi.wisc.edu}}
\newcommand{\af}{\rho}
\newcommand{\mets}{MET-hrs./week}
\newcommand{\pEm}[1]{$\mathrm{PM}_{#1}$}
\newcommand{\vmt}{$\mathrm{VMT}$}

\begin{document}
\firstpage{1}

@@

\subsection{Active Transport}

@@

\subsection{Road Injuries}

\col[red]{\textit{
We chose to model road injuries in a more simplifed manner than the
authors of ITHIM.  The original ITHIM requires information about the
transportational infrastructure that cannot be accurately modeled on a
regional level, and is more well-suited to say a collection of
counties as a case study. \cite{maizlish2013}  We use the overall percent
of travel by walking and road fatalities per U.S. metropolitan area to
estimate road fatalaties in U.S. metropolitan areas given the percent
of travel by walking. \cite{UWTechReport}
}}

\col[red]{\textit{
We need to estimate the increase/decrease in road injuries/fatalaties
nation-wide as walking/cycling time increases.  We need a relative
risk of road fatalaty as a function of active transport time...
}}

\col[red]{\textit{

}}

\subsection{Air Pollution}

Can we model the decrease in \pEm{2.5} nationally as a function of
decrease in driving time?  The original plan was to use a baseline
value for \pEm{2.5} and a linear relationship bewteen change in
\pEm{2.5} and change in \vmt{}.

@@

%\bibliographystyle{natbib}
\bibliographystyle{bmc_article}
%\bibliographystyle{mypapers}
\bibliography{ITHIM}
\end{document}
